On the Synchronization Power of the Openflow Data Plane

### 2015-03-29 inband-sync.tex
first full iteration finished

@@

\paragraph{Our Contributions}
This paper shows how to implement a very powerful transactional interface
 for software-defined networks. 
 Concretely, our implementation is based on
 standard Openflow~\cite{of-spec} primitives, which by themselves are very limited.
For example, we find that while Openflow's \emph{bundle} or \emph{rule overlap check}
features can serve as synchronization primitives,
without further mechanisms, their use is very limited:
with a bundle alone it is not possible to react to
and change switch configuration state in any non-trivial way,
and with the rule overlap check it is not possible to react to
update conflicts defined over non-overlapping flow spaces.
Moreover, we show that many powerful synchronous operations
can also be implemented without bundles.

@@

In the remainder of this paper, we will use the notation 
$\textbf{bundle}\{\;\ldots\;\}$ to refer to represent a
sequence of commands in a bundle.
\stefan{liron: i think the following needs more details $:-)$ :} A bundle will always have the following structure:
it first contains a \emph{send message} to start bundle,
followed by a sequence of messages wrapped in bundle and bundle ID, 
and finally end bundle control message for commit.
A bundle always returns a binary result: \emph{error} or \emph{success}.

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\columnwidth]{loadbal.pdf}~~
\includegraphics[width=0.8\columnwidth]{pic.pdf}\\
\caption{\emph{Left:} Load-balancing gone wrong. \emph{Right:} Illustration of transactional abstraction which  allows
controllers to modify switch configurations in complex ways,
and
depending on other flow spaces. Colors indicate different actions.}\label{fig:illu}
\end{figure*}

@@

@@

Every policy is associated with a \emph{policy identifier}
In the algorithm, the controller first reads the currently installed
policy, then choose a new unique policy, checks whether the new
policy and the current policy can be composed and, if so, replaces the
current policy with the composition. If, meanwhile, a new
policy (with a different identifier) has been installed, the update
fails and takes no effect.

>>>>

we add all rules of the policy also! but we could add rules before and only activate later => set selector later (maybe set timeout); transaction size constant => keep bundle small important: packet atomicity so maybe on hold during bundle

@@

\paragraph{Our Contributions}
This paper shows how to implement a very powerful transactional interface
 for software-defined networks. 
 Concretely, our implementation is based on
 standard Openflow~\cite{of-spec} primitives, which by themselves are very limited.
For example, we find that while Openflow's \emph{bundle} or \emph{rule overlap check}
features can serve as synchronization primitives,
without further mechanisms, their use is very limited:
with a bundle alone it is not possible to react to
and change switch configuration state in any non-trivial way (a bundle
essentially represents a single switch interaction),
and with the rule overlap check it is not possible to react to
update conflicts defined over non-overlapping flow spaces.
Moreover, we show that many powerful synchronous operations
can also be implemented without bundles.

@@

In the remainder of this paper, we will use the notation 
$\textbf{bundle}\{\;\ldots\;\}$ to refer to represent a
sequence of commands in a bundle.
\stefan{liron: i think the following needs more details $:-)$ :} A bundle will always have the following structure:
it first contains a \emph{send message} to start bundle,
followed by a sequence of messages wrapped in bundle and bundle ID, 
and finally end bundle control message for commit.
A bundle always returns a binary result: \emph{error} or \emph{success}.
Concretely, a transaction can represent between two to five switch interactions:
if limited space, Algo 7: read, claim id, read again, transaction, unclaim;
if if unlimited space: alg 6 is unbounded, increase policy ID by one.
transactions = five switch interactions , claim pid (line 5+6) together in bundle => one iteraction less?

In general, it is desirable to minimize the number of transactions \stefan{stefan should cite \cite{Jin2014Dionysus} here}

@@

\begin{figure*}[t]
\centering
\includegraphics[width=0.35\columnwidth]{loadbal-before.pdf}~\includegraphics[width=0.35\columnwidth]{loadbal.pdf}~~
\includegraphics[width=0.8\columnwidth]{pic.pdf}\\
\caption{\emph{Left:} Load-balancing gone wrong. \emph{Right:} Illustration of transactional abstraction which  allows
controllers to modify switch configurations in complex ways,
and
depending on other flow spaces. Colors indicate different actions. \stefan{lets make two real transactions: one bundle and one 2 or 5 interactions?}}\label{fig:illu}
\end{figure*}

@@

\stefan{liron: maybe we can make a more concrete example like we had it in medieval?}

@@

Every policy is associated with a \emph{policy identifier}.
In the algorithm, the controller first reads the currently installed
policy, then choose a new unique policy, checks whether the new
policy and the current policy can be composed and, if so, replaces the
current policy with the composition. If, meanwhile, a new
policy (with a different identifier) has been installed, the update
fails and takes no effect.
